---
title: "discogger"
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  message = FALSE, warning = FALSE
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/ewenme/discogger.svg?branch=master)](https://travis-ci.org/ewenme/discogger)

Tools for working with the [Discogs](https://www.discogs.com) API in R.

Discogs Developers Site: [https://www.discogs.com/developers](https://www.discogs.com/developers)

## Install

Development version

```{r install_dev, eval=FALSE}
devtools::install_github('ewenme/discogger')
```

## Authenticate

1. [Create a Discogs API v2 application](https://www.discogs.com/settings/developers)
2. Generate a personal access token from your [API application page](https://www.discogs.com/settings/developers)
3. Set your credentials in the System Environment variable `DISCOGS_API_TOKEN` by calling the `discogs_api_token()` function and entering your Discogs application personal access token when prompted.

## Use

```{r}
library(discogger)
library(tidyverse)
```

### Who released the most Dance Mania records?

```{r}
# get dance mania records listed on discogs
dm_recs <- discogs_label_releases(label_id = 314)

dm_recs$content %>%
  group_by(artist) %>%
  summarise(n_releases = n_distinct(catno)) %>%
  arrange(desc(n_releases)) %>%
  top_n(10)
```

## Contribute

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
